---
title: "Homework3 - Practice with Control Flow and Functions" author: "Upendra
Joshi" format: html editor: visual
---
In this homework I will practice about Control Flow and how to write Function.
Functions enhances efficiency in R programming. But First lets practice Control
Flow 

## Task 1: Control Flow 
We can take out old data from Homework 2 and load it here. Make sure that the file "hw2_list.rda" is in the working directory. Now load the file in the R environment

```{r}
load("hw2_list.rda")
head(bp_list)
str(bp_list)
df_bp = bp_list
```
The "bp_list" file is in the environment 

1) Suppose we want to characterize the post-treatment (or placebo) blood pressure measurement as
optimal (≤ 120), borderline (120 < bp ≤ 130), and high (> 130). First, create a new column
in each data frame from above called status. You can do this via


```{r}
df_bp$treatement$status <- character(20) #as we have 20 observations (see str ouptut above) I used 20 here
df_bp$placebo$status <- character(10)
head(df_bp)
str(df_bp)
```
2) For the non-placebo data frame (within the list), create a for loop and use if/then/else logic to
create the status column’s values.

```{r}

```

